Modal Abstractions for Virtualizing Memory Addresses

### 2024-07-04 examples.tex
before the last check on mapapage

\newcommand{\fpaddr}{\texttt{fpaddr}}
\newcommand{\specline}[1]{{\color{blue}\left\{#1\right\}}}
\newcommand{\sumapacesfull}[2]{
  \ownGhost\gammaPreds{\authfull{\singletonMap{#1}{#2}}}
}
\todo{ismail change the following spec base on the changes you have in the code}
\begin{figure}\footnotesize
  \begin{lstlisting}[mathescape]
;;complstatus_t vaspace_mappage(pte_t *pml4, void *va,uintptr_t pa, uint64_t perm ) {
...
;;setting up the stack      
;;char *a; pte_t *pte;
;;a = (char *)PGROUNDUP((uintptr_t)va);
 $\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,m)  \ast  \texttt{r14}\mapsto_{\textsf{r}} \_ \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{\textsf{r}} \_ \ast \ulcorner \texttt{aligned va} \land  \theta \; !!\; \vaddr = \texttt{None}\urcorner}_{\rtv}$
;;pte = walkpgdir_succ(pml4, a);
call pte_walkpgdir ;; Returns the virtual address of the L1 entry in rax

;;char *a; pte_t *pte;
;;a = (char *)PGROUNDUP((uintptr_t)va);
mov    -0x10[rbp],rcx
add    0x1000,rcx
sub    0x1,rcx
and    0xfffffffffffff000,%rcx
mov    rcx,-0x28[rbp]

;;pte = walkpgdir_succ(pml4, a);
mov    -0x8[rbp],rdi
mov    -0x28[rbp],rsi
mov    0x0,rax
callq  291 <vaspace_mappage+0x41>	28d: R_X86_64_PLT32	walkpgdir_succ-0x4
xor    r8,r8
movslq eax,rcx
mov    rcx,-0x30[rbp]

;;pte->writable     = PTE_WRITEABLE_SET(perm);
pte->user_acc     = PTE_USER_ACC_SET(perm);
;;pte->writethrough = PTE_WRITETHRU_SET(perm);
;;pte->nocache      = PTE_NOCACHE_SET(perm);
pte->pfn          = PTE_ADDR_TO_PFN(pa);
mov    -0x18[rbp],rcx
shr    0xc,rcx
mov    -0x30[rbp],rdx
mov    [rdx],rsi
movabs 0xffffffffff,rdi
and    rdi,rcx
shl    0xc,rcx
movabs 0xfff0000000000fff,rdi
and    rdi,rsi
or     rcx,rsi
mov    rsi,[rdx]
;;pte->nx           = PTE_NX_SET(perm);
;;pte->present      = 1;
;;clean up the stack and return
  \caption{Specification and proof of code for mapping a new page.}
\label{fig:mapping_code}

@@

>>>>

\newcommand{\fpaddr}{\texttt{fpaddr}}
\newcommand{\specline}[1]{{\color{blue}\left\{#1\right\}}}
\newcommand{\sumapacesfull}[2]{
  \ownGhost\gammaPreds{\authfull{\singletonMap{#1}{#2}}}
}
\todo{ismail change the following spec base on the changes you have in the code}
\begin{figure}\footnotesize
  \begin{lstlisting}[mathescape]
;;complstatus_t vaspace_mappage(pte_t *pml4, void *va,uintptr_t pa, uint64_t perm ) {
...
;;setting up the stack      
;;char *a; pte_t *pte;
;;a = (char *)PGROUNDUP((uintptr_t)va);
 $\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,m)  \ast  \texttt{r14}\mapsto_{\textsf{r}} \_ \ast \texttt{rdi}\mapsto_{r} \vaddr \ast \texttt{rax}\mapsto_{\textsf{r}} \_ \ast \ulcorner \texttt{aligned va} \land  \theta \; !!\; \vaddr = \texttt{None}\urcorner}_{\rtv}$
;;char *a; pte_t *pte;
;;a = (char *)PGROUNDUP((uintptr_t)va);
mov    -0x10[rbp],rcx
add    0x1000,rcx
sub    0x1,rcx
and    0xfffffffffffff000,%rcx
mov    rcx,-0x28[rbp]

;;pte = walkpgdir_succ(pml4, a);
mov    -0x8[rbp],rdi
mov    -0x28[rbp],rsi
mov    0x0,rax
callq  291 <vaspace_mappage+0x41>	28d: R_X86_64_PLT32	walkpgdir_succ-0x4
mov    0x0,r8
movslq eax,rcx
mov    rcx,-0x30[rbp]
;;pte->writable     = PTE_WRITEABLE_SET(perm);
...
pte->user_acc     = PTE_USER_ACC_SET(perm);
...
;;pte->writethrough = PTE_WRITETHRU_SET(perm);
...
;;pte->nocache      = PTE_NOCACHE_SET(perm);
pte->pfn          = PTE_ADDR_TO_PFN(pa);
mov    -0x18[rbp],rcx
shr    0xc,rcx
mov    -0x30[rbp],rdx
mov    [rdx],rsi
movabs 0xffffffffff,rdi
and    rdi,rcx
shl    0xc,rcx
movabs 0xfff0000000000fff,rdi
and    rdi,rsi
or     rcx,rsi
mov    rsi,[rdx]
;;pte->nx           = PTE_NX_SET(perm);
;;pte->present      = 1;
;;clean up the stack and return
...
;;}
\end{lstlisting}
  \caption{Specification and proof of code for mapping a new page.}
\label{fig:mapping_code}
\end{figure}

@@

\begin{comment}    
\end{comment}
